Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-17 paper.tex
Remove commented-out figures
update graphs

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{newunicodechar}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage[noend]{algorithm2e}
\usepackage{siunitx}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=16,
        ymin=2^3, ymax=2^13,
        xtick={1,2,4,8,16},
        ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 7.663472) (2, 9.354750) (4, 15.768194) (8, 104.921791) (16, 1882.683111)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.308541) (2, 10.704638) (4, 16.274305) (8, 38.800833) (16, 179.697681)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 10.591138) (2, 23.881333) (4, 142.013389) (8, 1676.148375) (16, 24327.359417)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 13.974694) (2, 26.216833) (4, 68.953444) (8, 245.601028) (16, 1028.670680)
          };
      \end{axis}
    \end{tikzpicture}
  \end{center}
  \caption{Results of the transitivity benchmark. TODO detailed description}%
  \label{fig:trans}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
        xlabel={Number of Rules},
        ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=2^3, ymax=1700,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]

        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 10.399958) (2, 16.426541) (4, 43.461403) (8, 205.595541) (16, 1238.090889) (32, 8927.857819)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 11.231875) (2, 12.879500) (4, 16.851930) (8, 24.666485) (16, 42.054055) (32, 76.369778)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 19.405222) (2, 33.487472) (4, 80.107597) (8, 284.954791) (16, 1536.089624) (32, 10721.729861)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.892069) (2, 40.031930) (4, 69.446902) (8, 130.640986) (16, 260.653917) (32, 481.827902)
          };
      \end{axis}
    \end{tikzpicture}
  \end{center}
  \caption{Results of the independence benchmark. TODO detailed description}%
  \label{fig:indep}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=6, ymax=20,
        xtick={1,2,3,4,5,6},
        ytick={10,15},
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 6.407973) (2, 9.831676) (3, 10.301718) (4, 10.626144) (5, 11.261754) (6, 11.795240)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 15.835558) (2, 16.961994) (3, 16.424259) (4, 17.605449) (5, 15.691536) (6, 14.982820)
          };
        \addlegendentry{incremental}
      \end{axis}
    \end{tikzpicture}
  \end{center}
  \caption{Results of the depth benchmark. TODO detailed description}%
  \label{fig:erase}
\end{figure}

@@

% \begin{figure}
%     % This is the erase without precompilation for 6 premises.
%     % Note I have a decent idea that would allow us to compare for multiple
%     % number of premises. 
%     % (Divide by the average of the stateful time to normalize.)
%     \begin{tikzpicture}
%         \begin{axis}[
%             title={Depth Test},
%             xlabel={Depth},
%             ylabel={Time in ms},
%             xmin=0, xmax=6,
%             ymin=50, ymax=65,
%             xtick={0,1,2,3,4,5,6},
%             ytick={50,55,60,65},
%             legend pos=north west,
%             ymajorgrids=true,
%             grid style=dashed,
%         ]

%         \addplot[
%             color=orange,
%             mark=square,
%             ]
%             coordinates {
%             (1,50.91)(2,53.14)(3,52.91)(4,51.22)(5,55.14)(6,56.60)
%             };
%             \addlegendentry{Stateless}

%         \addplot[
%             color=blue,
%             mark=square,
%             ]
%             coordinates {
%             (1,56.04)(2,56.43)(3,55.58)(4,55.26)(5,54.80)(6,60.61)
%             };
%             \addlegendentry{Stateful}

%         \end{axis}
%         \end{tikzpicture}
%     \end{figure}

%     \begin{figure}
%         % This is the erase without precompilation for 6 premises.
%         % Note I have a decent idea that would allow us to compare for multiple
%         % number of premises. 
%         % (Divide by the average of the stateful time to normalize.)
%         \begin{tikzpicture}
%             \begin{axis}[
%                 title={Scaled Depth Test},
%                 xlabel={Depth},
%                 ylabel={Time in ms},
%                 xmin=0, xmax=8,
%                 ymin=0.5, ymax=2,
%                 xtick={0,1,2,3,4,5,6,7,8},
%                 ytick={0.75,1,1.25,1.5,1.75},
%                 legend pos=north west,
%                 ymajorgrids=true,
%                 grid style=dashed,
%             ]

%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.883600)(1, 1.039751)};
%                 \addlegendentry{Stateless}
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.804521)(1, 1.017893)(2, 1.022493)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.791528)(1, 1.015467)(2, 1.076267)(3, 1.159999)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.743256)(1, 0.966436)(2, 1.058876)(3, 1.133514)(4, 1.225561)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.770625)(1, 1.003777)(2, 1.109929)(3, 1.215171)(4, 1.305373)(5, 1.390667)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.759093)(1, 1.016667)(2, 1.148273)(3, 1.213138)(4, 1.342795)(5, 1.442271)(6, 1.514877)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.709965)(1, 0.971294)(2, 1.068745)(3, 1.179333)(4, 1.312798)(5, 1.424054)(6, 1.551690)(7, 1.628344)};
%             \addplot[color=orange,mark=square,]
%                 coordinates {(0, 0.728860)(1, 1.001576)(2, 1.097472)(3, 1.219259)(4, 1.366683)(5, 1.444844)(6, 1.576972)(7, 1.668693)(8, 1.815399)};

%             \end{axis}
%             \end{tikzpicture}
%         \end{figure}

%                 \begin{figure}
%                     %Casacade with precompilation
%                         \begin{tikzpicture}
%                             \begin{axis}[
%                                 title={Casacade Test},
%                                 xlabel={Number of Rules},
%                                 ylabel={Time in ms},
%                                 xmin=0, xmax=32,
%                                 ymin=0, ymax=850,
%                                 ymode=log,xmode=log,
%                                 log basis x=2,
%                                 log basis y=2,
%                                 legend pos=north west,
%                                 ymajorgrids=true,
%                                 grid style=dashed,
%                             ]

%                             \addplot[
%                                 color=blue,
%                                 mark=square,
%                                 ]
%                                 coordinates {
%                                 (1, 0.393011)(2, 0.730952)(4, 1.327736)(8, 3.007961)(16, 10.173689)(32, 38.892027)
%                                 };
%                                 \addlegendentry{Stateful}

%                             \addplot[
%                                 color=orange,
%                                 mark=square,
%                                 ]
%                                 coordinates {
%                                 (1, 0.464973)(2, 0.759516)(4, 1.865191)(8, 7.585588)(16, 64.374740)(32, 813.336527)
%                                 };
%                                 \addlegendentry{Stateless}

%                             \end{axis}
%                             \end{tikzpicture}
%                         \end{figure}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{newunicodechar}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage[noend]{algorithm2e}
\usepackage{siunitx}
\usepackage{caption}
\usepackage{subcaption}

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of hypotheses},
        ylabel={Time in ms},
        xmin=1, xmax=16,
        ymin=2^3, ymax=2^13,
        xtick={1,2,4,8,16},
        ytick={2^3,2^5,2^7,2^9,2^11,2^13},
        xmode=log,
        ymode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 7.663472) (2, 9.354750) (4, 15.768194) (8, 104.921791) (16, 1882.683111)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 10.308541) (2, 10.704638) (4, 16.274305) (8, 38.800833) (16, 179.697681)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 10.591138) (2, 23.881333) (4, 142.013389) (8, 1676.148375) (16, 24327.359417)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 13.974694) (2, 26.216833) (4, 68.953444) (8, 245.601028) (16, 1028.670680)
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Transitivity benchmark}
    \label{fig:trans}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        xlabel={Number of Rules},
        %ylabel={Time in ms},
        xmin=1, xmax=32,
        ymin=2^3, ymax=1700,
        ymode=log,xmode=log,
        log basis x=2,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]

        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 10.399958) (2, 16.426541) (4, 43.461403) (8, 205.595541) (16, 1238.090889) (32, 8927.857819)
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 11.231875) (2, 12.879500) (4, 16.851930) (8, 24.666485) (16, 42.054055) (32, 76.369778)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 19.405222) (2, 33.487472) (4, 80.107597) (8, 284.954791) (16, 1536.089624) (32, 10721.729861)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.892069) (2, 40.031930) (4, 69.446902) (8, 130.640986) (16, 260.653917) (32, 481.827902)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Independence benchmark}
    \label{fig:indep}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in a context where there is a lot of work that can be reused (Transitivity) and no work to be reused (Independence). The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}
  \label{fig:benchmark}
  \end{figure}

@@

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=650,
        xtick={1,2,3,4,5,6},
        ytick={2^2,2^4,2^6,2^8},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 32.580083) (2, 33.212805) (3, 40.239833) (4, 47.670277) (5, 54.647458) (6, 61.044958) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 127.925541) (2, 140.497597) (3, 123.719264) (4, 130.819361) (5, 121.047667) (6, 123.789500)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 108.120444) (2, 107.352694) (3, 116.182833) (4, 125.995639) (5, 137.815527) (6, 142.310597) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 604.595791) (2, 624.541194) (3, 608.671111) (4, 614.285014) (5, 588.636819) (6, 595.276806) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Depth benchmark no-precompilation}
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        %ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=128,
        xtick={1,2,3,4,5,6},
        ytick={2^1,2^3,2^5,2^7},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 12.820514) (2, 12.645666) (3, 17.582138) (4, 22.730528) (5, 27.280097) (6, 32.578722) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.406416) (2, 13.747139) (3, 12.503764) (4, 12.950486) (5, 12.282083) (6, 12.151930) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 83.032819) (2, 79.396889) (3, 85.939180) (4, 92.495542) (5, 96.461291) (6, 105.517458)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.681583) (2, 25.322444) (3, 27.672833) (4, 26.999055) (5, 25.690319) (6, 25.257291)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Depth benchmark with precompilation}
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in depending on the \text{depth} of potential partial matches. The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}
  \label{fig:erase}
  \end{figure}

@@
